---
title: "Glyphosate-resistant Volunteer Corn Control"
author: "Vitor M. Anunciato"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#d00000",               # bright red
  inverse_background_color = "#f5f1e7", # dark dark blue
  inverse_header_color = "#c7c8ca",     # light aqua green
  inverse_text_color = "#fefdfa",       # white
  title_slide_background_color = "var(--base)",
  header_font_google = google_font("Raleway", "900"),
  text_font_google   = google_font("Fanwood", "300", "300i"),
  code_font_google   = google_font("Robot mono")
)
```

```{r echo=FALSE, warning=FALSE}
xaringanExtra::use_logo(
  image_url = "https://github.com/vitoranunciato/volunteercorncontrol/blob/main/docs/imagens/patlablogo.png?raw=true",
  link_url = "http://slides.yihui.name/xaringan",
  position = xaringanExtra::css_position(bottom = "1em", left = "1em")
)
```

**Interactions of Clethodim and Dicamba on Glyphosate-resistant Volunteer Corn Control**

"Vitor Muller Anunciato; Gabrielle de Castro Macedo; Daniel Araujo Doretto; Jeff A. Golus ; Caio A. Carbonari; Greg R. Kruger."

---
## Introduction

+ Common weed escape in soybean fields in Midwest and Mid-South.

+ Can reduce soybean yield through competition, cause problems with harvest,
host insects and diseases, and contaminate soybean seeds at the harvest.

+ Clethodim is known for its good grass control in post-emergence applications

+ However, antagonistic interactions have been reported when applied in tank-mixtures.

+ There is limited information on the efficacy of this tank-mixture on GRVC control.
---
## Objectives
• To evaluate the effects of this tank-mixture on GRVC control (F1 generation)
at different heights, with and without the use of non-ionic surfactant (NIS).

---
## Field Trial
+ Field planted at Dryland Farm. 25,000 seeds/acre (62,500 seeds/ha)

+ Plants heights: 12 in (30 cm), 24 in (60 cm) and 36 in (90 cm)

+ Split in plots with 10 x 30 ft each (3 x 10 m)

+ TTI 11002. 15 GPA (140 L/ha), 40 psi (276 KPa), 3.9 mph (6.3 km/h)

---
## Treatments
.pull-left[
**No R11 (NIS) in mixture 0.25% v/v**

**1.** Clethodim 76 g.i.a./ha

**2.** Clethodim 102 g.i.a./ha

**3.** Clethodim  136 g.i.a./ha

**4.** Clethodim 9 fl oz/a + Dicamba 560 g a.e./ha

**5.** Clethodim 12 fl oz/a + Dicamba 560 g a.e./ha

**6.** Clethodim 16 fl oz/a + Dicamba 560 g a.e./ha

**7.** Dicamba 560 g a.e./ha]

.pull-right[
**With R11 (NIS) in mixture 0.25% v/v**

**1.** Clethodim 76 g.i.a./ha

**2.** Clethodim 102 g.i.a./ha

**3.** Clethodim  136 g.i.a./ha

**4.** Clethodim 9 fl oz/a + Dicamba 560 g a.e./ha

**5.** Clethodim 12 fl oz/a + Dicamba 560 g a.e./ha

**6.** Clethodim 16 fl oz/a + Dicamba 560 g a.e./ha

**7.** Dicamba 560 g a.e./ha]

+ All solutions with Intact at 0.5% v/v

---

